Temporal Graph Cube

### 2023-01-26 TemporalGraphCube/TemporalGraphCube_revision.tex
response 1-27

Data warehouses and OLAP (Online Analytical Processing) techniques are helpful tools for knowledge workers (executive, manager, analyst) to analyze and make decisions, because Data warehouses and OLAP together can efficiently provide summarized information in different resolutions by specifying different views (different combinations of data dimensions) of large-scale real-world data through OLAP operations such as roll-up, drill-down and slice-and-dice \cite{chaudhuri1997overview}. Data warehouse built on traditional relational database (RDB) data is called data cube \cite{gray1997data}. In 2011, Zhao et al.\ \cite{zhao2011graph} proposed \kw{Graph} \kw{Cube} which extends data warehouses and OLAP techniques to analyze static multidimensional networks. For each query, static graph cube returns a static network with summarized information in its structure and statistical values on vertices and edges.

@@

Our work is also related to graph summarization and analysis. For static graphs, there are some representative works, including graph compression with MDL (Minimum Description Length) principle \cite{navlakha2008graph}, attributed graph compression \cite{wu2014graph} and graph clustering based on vertices partitioning \cite{zhou2009graph}. Recently, there exist several studies on static graph summarization, such as summarizing directed acyclic graph (DAG) \cite{zhu2020top}, summarizing multi-relation graph \cite{ke2022multi} where multiple edges of different types may exist between any pair of vertices, and DPGS model \cite{zhou2021dpgs}, which can preserve properties like graph spectrum and the authorities and hubnesses of vertices while reconstructing graph. \revision{However, all of them ignore the temporal information of big graph data}. For temporal graph and dynamic graph, TimeCrunch \cite{shah2015timecrunch} summarizes a large dynamic graph with a set of important temporal structures using MDL, such as ranged full clique, periodic bipartite core, oneshot star, etc. \revision{Some works summary graph streams into one sketche, e.g., \cite{mudannayake2021kmatrix,tang2016graph,ma2021parameter,ashrafi2021gs4,gou2019fast,chen2022scube}. \cite{fernandes2018dynamic,tsalouchidou2018scalable} use a sliding window of fixed length to only summarize the latest snapshots, and \cite{ko2020incremental} only summa}. However, in this paper, we can specify arbitrary time window to query summarized result in real time. In addition, we summarize the graph based on the selected dimensions of vertices, while the previous studies summarize the graph based on the super-node and super-edge. MoSSo \cite{} incrementally summarizes fully dynamic graph. The difference of \cite{ko2020incremental} with \cite{fernandes2018dynamic,tsalouchidou2018scalable} is that the edges in the graph are dynamically added and removed, and MoSSo incrementally summarizes the whole graph after any modification on the graph.

>>>>

Data warehouses and OLAP (Online Analytical Processing) techniques are helpful tools for knowledge workers (executive, manager, analyst) to analyze and make decisions, because Data warehouses and OLAP together can efficiently provide summarized information in different resolutions by specifying different views (different combinations of data dimensions) of large-scale real-world data through OLAP operations such as roll-up, drill-down and slice-and-dice \cite{chaudhuri1997overview}. Data warehouse built on traditional relational database (RDB) data is called data cube \cite{gray1997data}. In 2011, Zhao et al. \cite{zhao2011graph} proposed \kw{Graph} \kw{Cube} which extends data warehouses and OLAP techniques to analyze static multidimensional networks. For each query, static graph cube returns a static network with summarized information in its structure and statistical values on vertices and edges.

@@

Our work is also related to graph summarization and analysis. For static graphs, there are some representative works, including graph compression with MDL (Minimum Description Length) principle \cite{navlakha2008graph}, attributed graph compression \cite{wu2014graph} and graph clustering based on vertices partitioning \cite{zhou2009graph}. Recently, there exist several studies on static graph summarization, such as summarizing directed acyclic graph (DAG) \cite{zhu2020top}, summarizing multi-relation graph \cite{ke2022multi} where multiple edges of different types may exist between any pair of vertices, and DPGS model \cite{zhou2021dpgs}, which can preserve properties like graph spectrum and the authorities and hubnesses of vertices while reconstructing graph. \revision{However, all of them ignore the temporal information of big graph data}. For temporal graph and dynamic graph, TimeCrunch \cite{shah2015timecrunch} summarizes a large dynamic graph with a set of important temporal structures using MDL, such as ranged full clique, periodic bipartite core, oneshot star, etc. \revision{Some works (\cite{mudannayake2021kmatrix,tang2016graph,ma2021parameter,ashrafi2021gs4,gou2019fast,chen2022scube}) summarize graph stream into one sketche. \cite{fernandes2018dynamic,tsalouchidou2018scalable} use a sliding window of fixed length to only summarize the latest snapshots, and \cite{ko2020incremental} only summarize the current snapshot of a graph stream incrementally and losslessly}. However, in this paper, we can specify arbitrary time window to query summarized result in real time. \revision{Chen et al. \cite{chen2022horae} also studies summarizing snapshots in arbitrary time window, but they ignored the attributes of vertices and different views determined by combinations of those attributes}. We summarize graphs based on selected attributes of vertices, \revision{so we can get summarized information between vertices in different resolutions.}
